# Descriptives

```{r packages, include = FALSE}
library(knitr)
library(scales)
library(janitor)
library(gtsummary)
library(gt)
library(broom)
library(here)
library(lubridate)
library(ggtext)
library(ggstance)
library(patchwork)
library(showtext)
library(tidyverse)
```

```{r setup, include = FALSE}
# gtsummary table theme
theme_gtsummary_compact()

# Plotting options
Font <- "Titillium Web"
font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_family = Font,
    base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank()
    )
)
```


```{r}
data_path <- here("Data", "cleaned_data.rds")
if(file.exists(data_path)) {
  d <- read_rds(file = data_path)
} else {
  stop("'Data/cleaned_data.rds' doesn't exist, run `Analysis/data_cleaning.Rmd` to create it.")
}

# Make wave a nicely labelled factor
d <- d %>%
  mutate(Wave = factor(wid, levels = 1:3, labels = paste0("Wave ", 1:3)))
```

## Demographics before exclusions

```{r}
d %>%
  filter(wid == 1) %>% 
  distinct(pid, Game, Age, Experience, Gender) %>%
  select(-pid) %>%
  tbl_summary(by = Game, missing_text = "Missing") %>%
  add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_gt() %>% 
  tab_header(
    title = "Sample demographics",
    subtitle = "Inclusive of everyone before any exclusions"
  )
```

## Excluding participants

We exclude people who had no play during the study

```{r}
d %>% 
  distinct(Game, pid, Waves_with_play) %>% 
  mutate(Any_play = Waves_with_play > 0) %>% 
  select(-pid) %>% 
  tbl_summary(by = Game) %>% 
  add_overall()
# Filter by game for now because when telemetry is not provided its always zero. todo change this when data is in.
d <- d %>% 
  filter(
    !(Game %in% c(
      "AC:NH", "Apex Legends", 
      "Forza Horizon 4", "Gran Turismo Sport"
    ) & 
      Waves_with_play == 0)
  )
d %>% 
  distinct(Game, pid, Waves_with_play) %>% 
  mutate(Any_play = Waves_with_play > 0) %>% 
  select(-pid) %>% 
  tbl_summary(by = Game) %>% 
  add_overall()
```

We then exclude players who had no survey responses

```{r}
d %>% 
  distinct(Game, pid, Waves_with_response) %>% 
  mutate(Any_response = Waves_with_response > 0) %>% 
  select(-pid) %>% 
  tbl_summary(by = Game) %>% 
  add_overall()
d <- filter(d, Waves_with_response > 0)
d %>% 
  distinct(Game, pid, Waves_with_response) %>% 
  mutate(Any_response = Waves_with_response > 0) %>% 
  select(-pid) %>% 
  tbl_summary(by = Game) %>% 
  add_overall()
```

## Demographics after exclusions

```{r}
d %>%
  filter(wid == 1) %>% 
  distinct(pid, Game, Age, Experience, Gender) %>%
  select(-pid) %>%
  tbl_summary(by = Game, missing_text = "Missing") %>%
  add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_gt() %>% 
  tab_header(
    title = "Sample demographics",
    subtitle = "Inclusive of everyone after exclusions"
  )
```

## Survey descriptives

These are for people after exclusions.

### Response rate & retention

```{r}
# Get data on invite dates and Ns
invites <- read_csv(here("Data", "invites.csv")) %>% 
  rename(Game = game)
# Create a table where wave 0 are number of invites,
# then calculate response rate / retention at each wave.
# This assumes there are no new participants at wave 3
# (people who didn't participate in wave 2 showed up at wave 3).
bind_rows(
  select(invites, -date), 
  d %>% filter(Responded) %>% count(Game, wid)
) %>%
  arrange(Game, wid) %>%
  group_by(Game) %>%
  mutate(
    R_rate = percent(n / lag(n), .1),
    n = comma(n)
  ) %>%
  pivot_wider(names_from = wid, values_from = c(n, R_rate)) %>%
  mutate(
    Invites = n_0,
    `Wave 1` = str_glue("{n_1} ({R_rate_1})"),
    `Wave 2` = str_glue("{n_2} ({R_rate_2})"),
    `Wave 3` = str_glue("{n_3} ({R_rate_3})")
  ) %>%
  select(Game, Invites:`Wave 3`) %>%
  mutate(across(everything(), ~ str_replace(., "NA", "0"))) %>%
  kable(caption = "Number of people (response/retention rate) participating at each wave.")
```

### Response dates

Only for actual responses (not rows where survey date was filled to be able to join telemetry)

```{r}
d %>%
  filter(Responded) %>% 
  mutate(Date = as_date(StartDate)) %>%
  count(Game, Wave, Date) %>%
  ggplot(
    aes(Date, n, fill = Wave)
  ) +
  geom_col() +
  scale_y_continuous(
    "Responses",
    breaks = pretty_breaks(10),
    expand = expansion(c(0, .1)),
  ) +
  scale_x_date(
    "Date",
    date_breaks = "7 day", date_labels = "%b %d", date_minor_breaks = "1 day"
  ) +
  # geom_text(aes(label = n), nudge_y = 10) +
  facet_wrap("Game", scales = "free_y", ncol = 1)
```

Response times in BST

```{r}
d %>% 
  filter(Responded) %>% 
  mutate(Hour = hour(StartDate)) %>%
  count(Game, Wave, Hour) %>%
  ggplot(aes(Hour, y = n, fill = Wave)) +
  scale_y_continuous(
    "Responses",
    breaks = pretty_breaks(10),
    expand = expansion(c(0, .1)),
  ) +
  scale_x_continuous(
    breaks = seq(0, 21, by = 3),
    expand = expansion(c(0.01)),
    labels = function(x) paste0(x, ":00")
  ) +
  geom_col() +
  facet_wrap("Game", scales = "free", ncol = 2)
```

#### Durations between waves

Participants could respond with variable delays due to variation in email schedules and late responding. So we also check the actual intervals between completing waves

```{r}
d %>%
  filter(Responded) %>%
  select(wid, Game, Interval) %>%
  group_by(Game, wid) %>%
  filter(wid > 1) %>%
  summarise(
    min = min(Interval, na.rm = TRUE) %>% round(1),
    q25 = quantile(Interval, .25, na.rm = TRUE) %>% round(1),
    median = median(Interval, na.rm = TRUE) %>% round(1),
    q75 = quantile(Interval, .75, na.rm = TRUE) %>% round(1),
    max = max(Interval, na.rm = TRUE) %>% round(1),
    n = n()
  ) %>%
  kable(caption = "Interval durations preceding waves 2 and 3.")
d %>%
  filter(Responded) %>%
  filter(Wave != "Wave 1") %>%
  mutate(Wave = fct_drop(Wave)) %>%
  ggplot(aes(Interval)) +
  geom_vline(xintercept = 14, size = .2) +
  geom_histogram(binwidth = 1, col = "white") +
  scale_y_continuous(
    "Count",
    expand = expansion(c(0, .1))
  ) +
  scale_x_continuous(
    "Days between responding",
    breaks = seq(0, 28, by = 7)
  ) +
  facet_grid(Game ~ Wave, scales = "free_y")
```

## Save excluded data

```{r}
write_rds(d, file = here("Data/excluded_data.rds"))
```
