# Descriptives

Load the required packages.

```{r packages, results = "hide", cache = FALSE}
library(knitr)
library(scales)
library(janitor)
library(gtsummary)
library(gt)
library(broom)
library(here)
library(lubridate)
library(ggtext)
library(ggstance)
library(patchwork)
library(showtext)
library(tidyverse)
```

Plot and table options.

```{r}
# gtsummary table theme
theme_gtsummary_compact()

# Plotting options
Font <- "Titillium Web"
font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_family = Font,
    base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank()
    )
)
```

We then load the previously cleaned data table.

```{r}
data_path <- here("Data", "cleaned_data.rds")
if(file.exists(data_path)) {
  d <- read_rds(file = data_path)
} else {
  stop(str_glue("{data_path} doesn't exist, run `01-clean.Rmd` to create it."))
}

# Make wave a nicely labelled factor
d <- d %>%
  mutate(Wave = factor(wid, levels = 1:3, labels = paste0("Wave ", 1:3)))
```

## Demographics after exclusions

```{r}
d %>%
  filter(wid == 1) %>% 
  distinct(pid, Game, Age, Experience, Gender) %>%
  select(-pid) %>%
  tbl_summary(by = Game, missing_text = "Missing") %>%
  add_overall() %>% 
  bold_labels() %>% 
  italicize_levels() %>% 
  as_gt() %>% 
  tab_header(
    title = "Sample demographics",
    subtitle = "Inclusive of everyone after exclusions"
  )
```

## Survey descriptives

These are for people after exclusions.

### Response rate & retention

```{r}
# Get data on invite dates and Ns
invites <- read_csv(here("Data", "invites.csv")) %>% 
  rename(Game = game) %>% 
  mutate(Game = str_replace(Game, "Animal Crossing: New Horizons", "AC:NH"))
# Create a table where wave 0 are number of invites,
# then calculate response rate / retention at each wave.
# This assumes there are no new participants at wave 3
# (people who didn't participate in wave 2 showed up at wave 3).
bind_rows(
  select(invites, -date), 
  d %>% filter(Responded) %>% count(Game, wid)
) %>%
  arrange(Game, wid) %>%
  group_by(Game) %>%
  mutate(
    R_rate = percent(n / lag(n), .1),
    n = comma(n)
  ) %>%
  pivot_wider(names_from = wid, values_from = c(n, R_rate)) %>%
  mutate(
    Invites = n_0,
    `Wave 1` = str_glue("{n_1} ({R_rate_1})"),
    `Wave 2` = str_glue("{n_2} ({R_rate_2})"),
    `Wave 3` = str_glue("{n_3} ({R_rate_3})")
  ) %>%
  select(Game, Invites:`Wave 3`) %>%
  mutate(across(everything(), ~ str_replace(., "NA", "0"))) %>%
  kable(caption = "Number of people (response/retention rate) participating at each wave.")
```

### Response dates

Only for actual responses (not rows where survey date was filled to be able to join telemetry)

```{r fig.height = 8}
d %>%
  filter(Responded) %>% 
  mutate(Date = as_date(StartDate)) %>%
  count(Game, Wave, Date) %>%
  ggplot(
    aes(Date, n, fill = Wave)
  ) +
  geom_col() +
  scale_y_continuous(
    "Responses",
    breaks = pretty_breaks(10),
    expand = expansion(c(0, .1)),
  ) +
  scale_x_date(
    "Date",
    date_breaks = "7 day", date_labels = "%b %d", date_minor_breaks = "1 day"
  ) +
  # geom_text(aes(label = n), nudge_y = 10) +
  facet_wrap("Game", scales = "free_y", ncol = 1)
```

Response times

```{r fig.height = 8, fig.width = 8}
d %>% 
  filter(Responded) %>% 
  mutate(Hour = hour(StartDate)) %>%
  count(Game, Wave, Hour) %>%
  ggplot(aes(Hour, y = n, fill = Wave)) +
  scale_y_continuous(
    "Responses",
    breaks = pretty_breaks(10),
    expand = expansion(c(0, .1)),
  ) +
  scale_x_continuous(
    breaks = seq(0, 21, by = 3),
    expand = expansion(c(0.01)),
    labels = function(x) paste0(x, ":00")
  ) +
  geom_col() +
  facet_wrap("Game", scales = "free", ncol = 2)
```

#### Durations between waves

Participants could respond with variable delays due to variation in email schedules and late responding. So we also check the actual intervals between completing waves. Very small values are possible because a participant could have e.g. completed both waves 2 and 3 in succession after receiving wave 3 invitation. Note that negative values were also possible for this reason but they were excluded before.

```{r fig.width = 8, fig.height = 8}
d %>%
  select(Wave, Game, interval) %>%
  # group_by(Wave) %>%
  filter(Wave != "Wave 1") %>%
  summarise(
    Value = quantile(
      interval, 
      probs = c(0, .10, .25, .5, .75, .90, 1), 
      na.rm=T
    ) %>% 
      round(3),
    Quantile = percent(c(0, .10, .25, .5, .75, .90, 1))
  ) %>% 
  pivot_wider(names_from = Quantile, values_from = Value) %>% 
  kable(caption = "Interval duration percentiles preceding waves 2 and 3.")
d %>%
  filter(Wave != "Wave 1") %>%
  mutate(Wave = fct_drop(Wave)) %>%
  ggplot(aes(interval)) +
  geom_vline(xintercept = 14, size = .2) +
  geom_histogram(binwidth = 1, col = "white") +
  scale_y_continuous(
    "Count",
    expand = expansion(c(0, .1))
  ) +
  scale_x_continuous(
    "Days between responding",
    breaks = seq(0, 28, by = 7)
  ) +
  facet_grid(Game ~ Wave, scales = "free_y")
```

## System information

```{r}
library(sessioninfo)
session_info()
```
