# Main analysis

```{r packages, include = FALSE}
library(knitr)
library(scales)
library(janitor)
library(ggbeeswarm)
library(gtsummary)
library(bayestestR)
library(brms)
library(tidybayes)
library(broom)
library(here)
library(lubridate)
library(naniar)
library(ggtext)
library(emmeans)
library(ggstance)
library(ggdist)
library(patchwork)
library(readxl)
library(lavaan)
library(GGally)
library(ggnewscale)
library(showtext)
library(multidplyr)
library(tidyverse)
```

```{r setup, include=FALSE}
# parallel computations
cluster <- new_cluster(parallel::detectCores(logical = FALSE))
# load packages on clusters
cluster_library(cluster, c("dplyr", "lavaan"))

# MCMC settings
options(mc.cores = 4)
if (require("cmdstanr")) options(brms.backend = "cmdstanr")

# Run this to delete fitted models and refit
# unlink(list.files(pattern = "brm-.*\\.rds"))

# Plotting options
Font <- "Titillium Web"
font_add_google(Font, Font)
theme_set(
  theme_linedraw(
    base_family = Font,
    base_size = 12) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank()
    )
)
```

```{r}
data_path <- here("Data", "excluded_data.rds")
if(file.exists(data_path)) {
  d <- read_rds(file = data_path)
} else {
  stop("'Data/excluded_data.Rds' doesn't exist, run `Analysis/descriptive.Rmd` to create it.")
}
```

todo basically double check everything 

## Change this

Just keep games with telemetry

```{r}
d <- d %>% 
  filter(
    Game %in% c(
        "AC:NH", 
        "Apex Legends", 
        "Forza Horizon 4", 
        "Gran Turismo Sport"
      )
  )
```

## Univariate analyses

For all analyses, game time indicates average number of hours per day. The telemetry indicates total hours in the two week window, so we divide that by 14 to talk about average hours per day.

```{r}
d <- d %>% 
  mutate(Hours = Hours / 14)
```


### Key variables over time

Note that `played` variable is not useful; it was not collected in waves 2 and 3, and sometimes people did estimate to have time played even though reported not playing :/ 
We cut the figure for hours at some reasonable value.

```{r}
d %>%
  mutate(Hours_over_3 = Hours > 3) %>%
  tabyl(Hours_over_3) %>%
  adorn_pct_formatting()
```

```{r}
tmp <- d %>%
  select(
    Game, Wave, pid,
    Hours, CSAS, SPANE,
    Enjoyment, Extrinsic
  ) %>%
  pivot_longer(Hours:Extrinsic) %>%
  drop_na(value) %>%
  filter(!(name=="Hours" & value > 3)) %>%
  mutate(
    name = factor(
      name,
      levels = c("Hours", "SPANE", "CSAS", "Enjoyment", "Extrinsic"),
      labels = c("Hours played", "Affect", "Life satisfaction", "Intrinsic", "Extrinsic")
    )
  )

col1 <- "#2980b9"
col2 <- "#2980b9"

tmp %>%
  ggplot(
    aes(
      Wave, 
      value,
      fill = Game, 
      color, Game,
      group = Game
    )
  ) +
  scale_x_discrete(labels = 1:3, expand = expansion(c(0.1, .1))) +
  scale_color_manual(
    values = c(col1, col2, col1, col2, col1, col2, col1), 
    aesthetics = c("fill", "color", "slab_color")) +
  scale_y_continuous(
    "Value",
    breaks = pretty_breaks(),
    expand = expansion(.025)
  ) +
  geom_blank() +
  stat_halfeye(
    alpha = .33,
    height = .02,
    normalize = "panels", 
    adjust = 1.1,
    point_interval = NULL, 
    show.legend = FALSE
  ) +
  # only the outline (hackish)
  stat_halfeye(
    alpha = 1,
    height = .02,
    normalize = "panels", 
    aes(slab_color = Game),
    slab_size = 0.5,
    fill = NA,
    adjust = 1.1,
    point_interval = NULL, 
    show.legend = FALSE
  ) +
  stat_summary(
    fun.data = mean_cl_normal, 
    fatten = 1.25
  ) +
  stat_summary(
    fun = mean, 
    geom = "line",
    size = .33
  ) +
  facet_grid(name ~ Game, scales = "free_y") +
  theme(
    legend.position = "none", 
    strip.text.x = element_text(size = 8)
  )
ggsave(
  here("Output/Figures/Figure-Variables-Over-Time.png"), 
  width = 8, 
  height = 7
)
```

Then take a look at a simple model of change over time for each variable. Note that we can't use varying slopes with lmer because there's not enough data, so just random intercepts for games and players.

```{r}
library(lme4)
library(broom.mixed)
parameters_change_over_time <- d %>% 
  select(Game, pid, wid, Hours, Intrinsic = Enjoyment, Extrinsic, CSAS, SPANE) %>% 
  # Put intercept at first wave
  mutate(Wave = wid-1) %>% 
  pivot_longer(Hours:SPANE, names_to = "Variable") %>% 
  group_by(Variable) %>% 
  summarise(
    lmer(value ~ Wave + (1 | Game/pid), data = cur_data()) %>% 
      tidy(., "fixed", conf.int = TRUE)
  )
parameters_change_over_time %>% 
  mutate(across(where(is.numeric), ~format(round(.x, 2), nsmall=2))) %>% 
  mutate(Result = str_glue("{estimate}, 95%CI [{conf.low}, {conf.high}]")) %>% 
  select(Variable, term, Result) %>% 
  pivot_wider(names_from = term, values_from = Result)
```


## Models

### Simple correlation

A new data frame for e.g. regression models

```{r}
d_model <- d %>%
  select(
    Game, pid, wid, Wave, Hours, SPANE, CSAS, 
    Intrinsic = Enjoyment, Extrinsic
  ) %>%
  arrange(Game, pid, Wave)
```

Regression coefficients (standardized and raw) of well-being predicted from game play need satisfaction, and intrinsic motivation (enjoyment).

```{r}
d_model %>%
  rename(Affect = SPANE, `Life satisfaction` = CSAS) %>%
  pivot_longer(
    c(Affect, `Life satisfaction`), 
    names_to = "Outcome", values_to = "Outcome_value"
  ) %>%
  pivot_longer(
    c(Hours, Intrinsic, Extrinsic), 
    names_to = "Predictor", values_to = "Predictor_value"
  ) %>% 
  group_by(Game, Outcome, Predictor, Wave) %>%
  summarise(
    std = list(tidy(lm(scale(Outcome_value) ~ scale(Predictor_value), data = cur_data()), conf.int = TRUE)),
    raw = list(tidy(lm(Outcome_value ~ Predictor_value, data = cur_data()), conf.int = TRUE)),
  ) %>%
  pivot_longer(std:raw, names_to = "Model") %>%
  unnest(value) %>%
  filter(term != "(Intercept)") %>%
  mutate(Panel = str_glue("{Outcome} ({Model})")) %>%
  mutate(
    Panel = factor(
      Panel,
      levels = c(
        "Affect (raw)", "Life satisfaction (raw)",
        "Affect (std)", "Life satisfaction (std)"
      )
    )
  ) %>%
  ggplot(aes(estimate, Game, col = Wave, shape = Model)) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  scale_x_continuous(
    "Bivariate regression coefficient (95%CI)",
    breaks = pretty_breaks()
  ) +
  geom_pointrangeh(
    aes(xmin = conf.low, xmax = conf.high),
    size = .4,
    position = position_dodge2v(.3)
  ) +
  facet_grid(Outcome~Predictor, scales = "free_x") +
  theme(
    axis.title.x = element_markdown(),
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.title = element_blank()
  )
```

## RICLPM

Wrangle data to a format where lavaan model is easier to map to variable pairs: Wide format with different rows for outcomes (well-being) and predictors (hours, needs, motivations).

```{r}
d_riclpm_long <- d %>%
  select(Game, pid, wid, Hours, Intrinsic = Enjoyment, Extrinsic, SPANE, CSAS) %>%
  # Long format on well-being scores (outcomes)
  pivot_longer(
    c(SPANE, CSAS), names_to = "y_var", values_to = "y"
  ) %>%
  # Long format on other variables (predictors)
  pivot_longer(
    c(Hours, Intrinsic, Extrinsic), 
    names_to = "x_var", values_to = "x"
  )
d_riclpm_wide <- d_riclpm_long %>% 
  pivot_wider(names_from = wid, values_from = c(x, y), names_sep = "")
```

### Some kind of data figure

```{r}
Order <- tibble(
  y_var = c("SPANE", "SPANE", "CSAS", "CSAS"),
  wid = c(2, 3, 2, 3),
  Panel = c(
    "Affect[plain('[Wave 2]')]",
    "Affect[plain('[Wave 3]')]",
    "LS[plain('[Wave 2]')]",
    "LS[plain('[Wave 3]')]"
  ),
  Panel_label = fct_inorder(Panel)
)

d_riclpm_plots <- d_riclpm_long %>% 
  arrange(Game, pid, x_var, wid) %>%
  group_by(Game, pid, x_var, y_var) %>%
  mutate(lag_x = lag(x)) %>%
  left_join(Order) %>% 
  ungroup() %>% 
  filter(wid > 1)

d_riclpm_plots %>% 
  filter(x_var == "Hours", lag_x <= 3) %>% 
  ggplot(aes(lag_x, y)) +
  scale_x_continuous(
    "Hours played per day at previous wave",
    breaks = pretty_breaks(3)
  ) +
  scale_y_continuous(
    "Well-being at current wave",
    breaks = pretty_breaks()
  ) +
  geom_point(size = .2, alpha = .2, shape = 1, col = col1) +
  geom_smooth(
    method = "gam", size = .4,
    color = "black",
    alpha = .33, show.legend = FALSE
  ) +
  facet_grid(
    Panel_label ~ Game, 
    scales = "free_y", 
    labeller = labeller(.rows = label_parsed)
  ) +
  theme(
    aspect.ratio = 1,
    panel.grid = element_blank(),
    strip.text.x = element_text(size = 8)
  )
ggsave(
  here("Output/Figures/Figure-WB-on-Hours.png"), 
  width = 8, 
  height = 5
)

# Plots with other predictors
p_tmp_1 <- last_plot() %+% 
  filter(d_riclpm_plots, x_var == "Intrinsic") +
  scale_x_continuous(
    "Intrinsic motivation at previous wave",
    breaks = pretty_breaks()
  )
p_tmp_1
ggsave(
  here("Output/Figures/Figure-WB-on-Intrinsic.png"), 
  width = 8, 
  height = 5
)
p_tmp_2 <- last_plot() %+% 
  filter(d_riclpm_plots, x_var == "Extrinsic") +
  scale_x_continuous(
    "Extrinsic motivation at previous wave",
    breaks = pretty_breaks()
  )
p_tmp_2
ggsave(
  here("Output/Figures/Figure-WB-on-Extrinsic.png"), 
  width = 8, 
  height = 5
)
# And together?
p_tmp_1 / p_tmp_2
ggsave(
  here("Output/Figures/Figure-WB-on-Intrinsic-and-Extrinsic.png"), 
  width = 8, 
  height = 9
)
```

### Fit one model to all data

First fit RICLPM to all data. Separately to the two well-being outcomes, and each predictor (hours, subjective scales). Constrain (cross)lagged parameters

Syntax based on <https://jeroendmulder.github.io/RI-CLPM/lavaan.html>

```{r}
riclpm_constrained <- "
  # Create between components (random intercepts)
  RIx =~ 1*x1 + 1*x2 + 1*x3
  RIy =~ 1*y1 + 1*y2 + 1*y3

  # Create within-person centered variables
  wx1 =~ 1*x1
  wx2 =~ 1*x2
  wx3 =~ 1*x3
  wy1 =~ 1*y1
  wy2 =~ 1*y2
  wy3 =~ 1*y3

  # Estimate the lagged effects between the within-person centered variables (constrained).
  wx2 ~ bx*wx1 + gx*wy1
  wy2 ~ gy*wx1 + by*wy1
  wx3 ~ bx*wx2 + gx*wy2
  wy3 ~ gy*wx2 + by*wy2

  # Estimate the covariance between the within-person centered
  # variables at the first wave.
  wx1 ~~ wy1 # Covariance

  # Estimate the covariances between the residuals of the
  # within-person centered variables (the innovations).
  wx2 ~~ wy2
  wx3 ~~ wy3

  # Estimate the variance and covariance of the random intercepts.
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2
  wx3 ~~ wx3
  wy3 ~~ wy3
"
```

```{r}
cluster_copy(cluster, "riclpm_constrained")
fit_riclpm_all <- d_riclpm_wide %>%
  group_by(y_var, x_var) %>%
  partition(cluster) %>%
  summarise(
    fit = lavaan(
      riclpm_constrained,
      data = cur_data(),
      missing = "ml",
      meanstructure = TRUE,
      int.ov.free = TRUE
    ) %>% list()
  ) %>% 
  collect()

get_lavaan_pars <- function(x) {
  bind_rows(
    parameterestimates(x) %>%
      mutate(Type = "Unstandardized"),
    standardizedsolution(x) %>%
      rename(est = est.std) %>%
      mutate(Type = "Standardized")
  ) %>%
    as_tibble() %>%
    unite("Parameter", c(lhs, op, rhs), sep = " ", remove = FALSE)
}

pars_riclpm_avg <- fit_riclpm_all %>%
  mutate(pars = map(fit, get_lavaan_pars)) %>%
  select(-fit)
```

```{r}
pars_riclpm_avg %>% 
  ungroup() %>% 
  unnest(pars) %>% 
  filter(
    Parameter %in% c("wy2 ~ wx1", "wx2 ~ wy1", "wy2 ~ wy1", "wx2 ~ wx1"), 
    Type == "Unstandardized"
  ) %>% 
  mutate(across(where(is.numeric), ~format(round(.x, 2), nsmall=2))) %>% 
  mutate(Result = str_glue("{est}, [{ci.lower}, {ci.upper}]")) %>% 
  select(y_var, x_var, Parameter, Result) %>% 
  pivot_wider(names_from = Parameter, values_from = Result)
```

### Separate models per game

Fit the above model separately to each game.

```{r}
fit_riclpm_sep <- d_riclpm_wide %>%
  group_by(y_var, x_var, Game) %>%
  partition(cluster) %>%
  summarise(
    fit = lavaan(
      riclpm_constrained,
      data = cur_data(),
      missing = "ml",
      meanstructure = TRUE,
      int.ov.free = TRUE
    ) %>% list()
  ) %>% 
  collect()
pars_riclpm_sep <- fit_riclpm_sep %>%
  mutate(pars = map(fit, get_lavaan_pars)) %>%
  select(-fit)
```

### Multi-group fit with parameter constraints

```{r}
riclpm_constrained_multigroup <- "
  # Create between components (random intercepts)
  RIx =~ 1*x1 + 1*x2 + 1*x3
  RIy =~ 1*y1 + 1*y2 + 1*y3

  # Create within-person centered variables
  wx1 =~ 1*x1
  wx2 =~ 1*x2
  wx3 =~ 1*x3
  wy1 =~ 1*y1
  wy2 =~ 1*y2
  wy3 =~ 1*y3

  # Estimate the lagged effects between the within-person centered variables (constrained)
  # such that each group gets their own coefs
  wx2 ~ c(bx1, bx2, bx3, bx4)*wx1 + c(gx1, gx2, gx3, gx4)*wy1
  wy2 ~ c(gy1, gy2, gy3, gy4)*wx1 + c(by1, by2, by3, by4)*wy1
  wx3 ~ c(bx1, bx2, bx3, bx4)*wx2 + c(gx1, gx2, gx3, gx4)*wy2
  wy3 ~ c(gy1, gy2, gy3, gy4)*wx2 + c(by1, by2, by3, by4)*wy2

  # Estimate the covariance between the within-person centered
  # variables at the first wave.
  wx1 ~~ wy1 # Covariance

  # Estimate the covariances between the residuals of the
  # within-person centered variables (the innovations).
  wx2 ~~ wy2
  wx3 ~~ wy3

  # Estimate the variance and covariance of the random intercepts.
  RIx ~~ RIx
  RIy ~~ RIy
  RIx ~~ RIy

  # Estimate the (residual) variance of the within-person centered variables.
  wx1 ~~ wx1 # Variances
  wy1 ~~ wy1
  wx2 ~~ wx2 # Residual variances
  wy2 ~~ wy2
  wx3 ~~ wx3
  wy3 ~~ wy3
"
```

```{r}
cluster_copy(cluster, "riclpm_constrained_multigroup")
fit_riclpm_mg <- d_riclpm_wide %>%
  group_by(y_var, x_var) %>%
  partition(cluster) %>%
  summarise(
    fit = lavaan(
      riclpm_constrained_multigroup,
      data = cur_data(),
      missing = "ml",
      group = "Game",
      # group.equal = c(
      #   "lv.variances", 
      #   "lv.covariances"
      # ),
      meanstructure = TRUE,
      int.ov.free = TRUE
    ) %>% list()
  ) %>% 
  collect()

pars_riclpm_mg <- fit_riclpm_mg %>%
  mutate(pars = map(fit, get_lavaan_pars)) %>%
  mutate(
    pars = map2(
      pars, fit,
      ~ left_join(
        .x, 
        tibble(
          group = 1:length(unique(d_riclpm_wide$Game)), 
          Game = .y@Data@group.label
        )
      )
    )
  ) %>%
  select(-fit)
```

Look at estimates

```{r}
# Table of RICLPM parameters from all models
pars_riclpm <- pars_riclpm_mg %>%
  unnest(pars) %>%
  group_by(y_var, x_var, Game) %>%
  nest() %>%
  rename(pars = data) %>%
  mutate(Model = "Multigroup") %>%
  bind_rows(pars_riclpm_sep %>% mutate(Model = "Independent")) %>%
  bind_rows(pars_riclpm_avg %>% mutate(Model = "Average", Game = "Average")) %>%
  ungroup() %>%
  unnest(pars) %>%
  # Take regression parameters at first interval, and 
  # covariance parameters of interest
  filter(
    (str_detect(Parameter, " ~ ") & !str_detect(Parameter, "3")) |
      Parameter %in% c("RIx ~~ RIy", "wx1 ~~ wy1", "wx2 ~~ wy2", "wx3 ~~ wy3")
  ) %>%
  mutate(Game = fct_relevel(Game, "Average")) %>% 
  select(-c(lhs:label, z))

# Plot of regression parameters (autocorrelations and crosslags; raw)
pars_riclpm %>%
  rename(Predictor = x_var, Outcome = y_var) %>% 
  filter(Outcome == "SPANE") %>% 
  filter(Type == "Unstandardized", str_detect(Parameter, " ~ ")) %>% 
  ggplot(
    aes(
      est, Game, 
      col = Model, xmin = ci.lower, xmax = ci.upper
    )
  ) +
  scale_x_continuous(
    "Estimated parameter",
    breaks = pretty_breaks()
  ) +
  geom_vline(xintercept = 0, size = .2, lty = 2) +
  geom_pointrangeh(position = position_dodge2v(.5), size = .4) +
  labs(subtitle = "SPANE") +
  facet_grid(Parameter ~ Predictor, scales = "free_x", labeller = label_both)

last_plot() %+%
  (pars_riclpm %>%
     rename(Predictor = x_var, Outcome = y_var) %>% 
     filter(Outcome == "CSAS") %>% 
     filter(Type == "Unstandardized", str_detect(Parameter, " ~ "))) +
  labs(subtitle = "CSAS")
```

Plots of covariance parameters (raw)

```{r}
last_plot() %+% 
  filter(
    pars_riclpm %>% rename(Predictor = x_var, Outcome = y_var), 
    Type == "Unstandardized", 
    str_detect(Parameter, " ~~ "),
    Outcome == "SPANE"
  ) + 
  labs(x = "Estimated LV covariance")
```

## Meta-analyses

Number of observations/participants per model

```{r}
fit_riclpm_sep %>%
  mutate(N = map_dbl(fit, nobs) %>% comma) %>% 
  select(-fit) %>% 
  pivot_wider(
    names_from = x_var, 
    values_from = N, 
    names_glue = "{x_var} {.value}"
  ) %>% 
  rename(Outcome = y_var) %>% 
  kable(caption = "Sample sizes per RICLPM")
```

Then conduct all meta-analyses (for each y_var-x_var pair, parameter of interest, and type of parameter (standardized, unstandardized)) for both multigroup and independent RICLPMs

```{r results='hide', cache = FALSE}
# Select variables from RICLPM parameters to data for MA
d_ma <- pars_riclpm %>%
  filter(
    Model == "Independent", 
    str_detect(Parameter, " ~ ")
  ) %>% 
  select(Type, y_var, x_var, Game, Parameter, est, se, ci.lower, ci.upper)

# This is how many meta-analyses will be conducted
distinct(d_ma, Type, y_var, x_var, Parameter)

# Compile meta-analytic brms/Stan model
bf_ma <- bf(est | se(se) ~ 0 + Intercept + (0 + Intercept | Game))
fit_ma_empty <- brm(
  bf_ma,
  data = d_ma,
  prior = prior(student_t(7, 0, 0.5), class = "sd", group = "Game") +
    prior(normal(0, 1), class = "b"),
  chains = 0,
  control = list(adapt_delta = .999),
  file = here("Output/brms/brm-ma-empty")
)

# Fit meta-analysis separately to each x-y pair X parameter X type X model
# by updating the compiled model
# cluster_library(cluster, c("brms", "here", "stringr"))
# cluster_copy(cluster, "fit_ma_empty")
fit_ma <- d_ma %>%
  group_by(x_var, y_var, Parameter, Type) %>%
  mutate(i = cur_group_id()) %>%
  # partition(cluster) %>%
  summarise(
    fit = list(
      update(
        fit_ma_empty,
        newdata = cur_data(),
        control = list(adapt_delta = .999),
        iter = 6500, warmup = 4000, 
        refresh = 0,
        file = here(str_glue("Output/brms/brm-ma-{unique(i)}"))
      )
    )
  ) %>% 
  # collect() %>% 
  ungroup()

# Function to get varying and average effects' posteriors from brmsfit
get_ma_post <- function(x) {
  coef(x, summary = FALSE) %>%
    .[["Game"]] %>%
    .[, , 1] %>%
    as.data.frame() %>%
    cbind(fixef(x, summary = FALSE)) %>% 
    as_tibble()
}
```

### Average effects

This figure shows the average (across games) effects from meta-analyses using the independent lavaan fits, multigroup lavaan fits, and from the completely pooled lavaan model (one model fit to all games' data). Unstandardized parameters are shown.

```{r}
ma_pars <- fit_ma %>% 
  mutate(out = map(fit, get_ma_post)) %>% 
  mutate(
    out2 = map(
      out, 
      ~describe_posterior(.x, centrality = "mean") %>% 
        rename(Game = Parameter)
    )
  ) %>% 
  select(-fit, -out) %>%
  unnest(out2) %>% 
  select(-CI, -starts_with("ROPE")) %>% 
  mutate(Game = str_replace(Game, "Intercept", "Average"))

ma_pars %>% 
  filter(Game == "Average", Type == "Unstandardized") %>% 
  ggplot(aes(Mean, Parameter)) +
  scale_x_continuous(
    "Estimated parameter (95%CI)",
    breaks = pretty_breaks()
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high)
  ) +
  geom_pointrangeh(
    data = pars_riclpm %>% 
      filter(
        str_detect(Parameter, " ~ "), 
        Type == "Unstandardized", 
        Model == "Average"
      ),
    aes(x = est, xmin = ci.lower, xmax = ci.upper, color = "Pooled"),
    position = position_nudge(y = .15)
  ) +
  facet_grid(y_var~x_var)
```

### Hours <-> WB

Draw a forest plot of meta-analyses with hours

```{r}
# Table of nice labels in proper order
Order <- distinct(fit_ma, x_var, y_var, Parameter) %>% 
  ungroup() %>% 
  # Meta-analyses only for regression parameters
  filter(str_detect(Parameter, " ~ ")) %>% 
  mutate(
    x_lab = case_when(
      x_var == "Hours" ~ "Play",
      x_var == "Intrinsic" ~ "Intrinsic",
      x_var == "Extrinsic" ~ "Extrinsic"
    ),
    y_lab = case_when(
      y_var == "SPANE" ~ "Affect",
      y_var == "CSAS" ~ "Life~satisfaction"
    ),
    Panel_label = case_when(
      Parameter == "wx2 ~ wx1" ~ 
        str_glue('{x_lab}[plain("[t-1]")]%->%{x_lab}[plain("[t]")]'),
      Parameter == "wy2 ~ wy1" ~ 
        str_glue('{y_lab}[plain("[t-1]")]%->%{y_lab}[plain("[t]")]'),
      Parameter == "wy2 ~ wx1" ~ 
        str_glue('{x_lab}[plain("[t-1]")]%->%{y_lab}[plain("[t]")]'),
      Parameter == "wx2 ~ wy1" ~ 
        str_glue('{y_lab}[plain("[t-1]")]%->%{x_lab}[plain("[t]")]')
    )
  ) %>% 
  mutate(
    Parameter_order = factor(
      Parameter, 
      levels = c("wy2 ~ wx1", "wx2 ~ wy1", "wy2 ~ wy1", "wx2 ~ wx1")
    )
  ) %>% 
  arrange(Parameter_order, desc(y_var)) %>% 
  mutate(Panel_label = fct_inorder(Panel_label))

#' Summarize meta-analyses
#' @param object a grouped df with all the brmsfits; e.g., fit_ma
#' 
#' @return a list with 
#'  - `summary`:
#'  - `draws`: the posterior draws
summarize_ma <- function(object) {
  
  # Data for plotting meta-analyses' posterior distributions
  p_data <- object %>%
    mutate(out = map(fit, get_ma_post)) %>%
    select(-fit) %>%
    unnest(out) %>%
    rename(Average = Intercept) %>%
    pivot_longer(`AC:NH`:Average, names_to = "Game") %>%
    mutate(Game = fct_relevel(Game, "Average")) %>%
    ungroup() %>%
    left_join(Order)
  
  # Summaries of posterior distributions
  fit_ma_sum <- p_data %>%
    group_by(y_var, x_var, Parameter, Type, Game, Panel_label) %>%
    summarise(
      describe_posterior(
        value,
        test = c("pd"),
        centrality = "mean"
      ) %>% select(-Parameter)
    ) %>%
    ungroup() %>%
    mutate(
      across(
        c(Mean, CI_low, CI_high),
        .fns = list(r = ~ format(round(., 2), nsmall = 2))
      )
    ) %>%
    mutate(Res = str_glue("{Mean_r} [{CI_low_r}, {CI_high_r}]")) %>%
    # Ordered labels
    left_join(Order) %>%
    mutate(Game = fct_relevel(Game, "Average"))
  
  list(
    summary = fit_ma_sum,
    draws = p_data
  )
}

#' Function to draw forest plots
#' @param object object created using `summarize_ma`
#' @param type
#' @param x_var
#' @param parameters
#' @param lavaan
#' 
#' @return a ggplot2 object
forest_plot <- function(
  object,
  type = "Unstandardized", 
  x_var = "Hours", 
  parameters = c("wy2 ~ wx1", "wx2 ~ wy1"),
  lavaan = FALSE
) {
  out <- object$summary %>%
    filter(
      Type == {{type}}, 
      x_var == {{x_var}}, 
      Parameter %in% {{parameters}}
    ) %>%
    # We can use the xintercept mapping to control alpha below
    ggplot(aes(Mean, Game)) +
    coord_cartesian(xlim = c(-.25, .35)) +
    scale_x_continuous(
      "Estimated cross-lagged effect",
      breaks = c(-.2, -.1, 0, .1, .2, .3),
      expand = expansion(.01)
    ) +
    scale_y_discrete(
      expand = expansion(c(0.15, 0.25)),
      labels = function(x) ifelse(x == "Average", "**Average**", x)
    ) +
    scale_fill_brewer(
      palette = "Set1", direction = 1, aesthetics = c("fill", "color")
    ) +
    scale_alpha_manual(values = c(.33, .66)) +
    # Vertical line for 0
    geom_vline(xintercept = 0, size = .1, col = "grey60") +
    # Posterior densities
    stat_halfeye(
      data = object$draws %>% 
        filter(
          Type == {{type}}, 
          x_var == {{x_var}}, 
          Parameter %in% {{parameters}}
        ),
      aes(
        value,
        fill = stat(x > 0),
        alpha = Game=="Average"
      ),
      height = .75, adjust = 1.5, point_interval = NULL,
      show.legend = FALSE, normalize = "panels"
    ) +
    # Summary geoms and texts
    geom_pointrangeh(
      aes(x = Mean, xmin = CI_low, xmax = CI_high),
      size = .5, fatten = 1.5
    ) +
    # CIs in right margin
    geom_text(
      vjust = -0.5, size = 3, hjust = 1,
      aes(x = .35, label = Res),
      family = Font
    ) +
    # Posterior probability of direction for average
    geom_text(
      data = object$summary %>%
        filter(Game == "Average") %>%
        filter(
          Type == {{type}}, 
          x_var == {{x_var}}, 
          Parameter %in% {{parameters}}
        ),
      vjust = 1.4, size = 3,
      aes(
        x = sign(Mean) * 0,
        hjust = ifelse(sign(Mean) == 1, 0, 1),
        label = str_glue("{percent(pd, .1)}"),
        col = as.logical(sign(Mean) == 1)
      ),
      family = Font,
      show.legend = FALSE
    ) +
    theme(
      axis.title.y = element_blank(),
      axis.text.y = element_markdown(),
      # panel.grid.major.y = element_blank()
    ) +
    facet_wrap("Panel_label", scales = "free_x", labeller = label_parsed)
  
  # Also display lavaan game-specific estimates?
  if (lavaan) {
    out +
      geom_pointrangeh(
        data = d_ma %>%
          filter(
            Type == {{type}}, 
            x_var == {{x_var}}, 
            Parameter %in% {{parameters}}
          ) %>%
          left_join(Order),
        col = "gray40", fatten = 1.25, size = .33,
        aes(x = est, xmin = ci.lower, xmax = ci.upper),
        position = position_nudge(y = -.075)
      )
  } else out
}
```

```{r}
fit_ma_sum <- summarize_ma(fit_ma)
forest_plot(
  object = fit_ma_sum,
  type = "Unstandardized", 
  x_var = "Hours",
  parameters = c("wy2 ~ wx1", "wx2 ~ wy1"),
  lavaan = FALSE
)
ggsave(here("Output/Figures/Figure-MA-WB-Hours.png"), width = 8, height = 5)
```

```{r}
# Also see in comparison to lavaan model estimates
forest_plot(
  object = fit_ma_sum,
  type = "Unstandardized", 
  x_var = "Hours",
  parameters = c("wy2 ~ wx1", "wx2 ~ wy1"),
  lavaan = TRUE
)
```

#### Some post-hoc calculations

What is the average wave-to-wave fluctuation in one's play, and how much would that impact wellbeing?

```{r}
# Average ranges of people's game-play
average_play <- d %>%
  group_by(Game, pid) %>% 
  summarise(Mean = mean(Hours, na.rm = T), Range = diff(range(Hours))) %>% 
  summarise(Mean = mean(Mean, na.rm = T), Range = mean(Range, na.rm = T)) %>% 
  mutate(Mean2 = mean(Mean, na.rm = T), Range2 = mean(Range, na.rm = T))
average_play

average_pw <- average_play$Range2 %>% unique

fit_ma %>% 
  filter(
    x_var == "Hours", 
    # y_var == "SPANE", 
    Type == "Unstandardized",
    Parameter == "wy2 ~ wx1"
  ) %>% 
  mutate(average_pw) %>% 
  mutate(
    hypothesis = map2(
      fit, 
      average_pw, 
      ~hypothesis(.x, str_glue("Intercept * {.y} = 0")) %>% .[[1]]
    )
  ) %>% 
  unnest(hypothesis) %>% 
  select(x_var, y_var, average_pw, Parameter, Estimate:CI.Upper) %>% 
  kable(digits = 3, caption = "ES of average hours per week on WB")
```


### Experiences <-> WB

These meta-analyses were conducted above. Now we just need to filter for the correct parameters for plots. They are also shown in the table above. Need to double check that everything has worked so these meta analyses are still a bit of WIP.

```{r}
forest_plot(
  object = fit_ma_sum,
  type = "Unstandardized", 
  x_var = "Intrinsic",
  parameters = c("wy2 ~ wx1", "wx2 ~ wy1"),
  lavaan = TRUE
)

forest_plot(
  object = fit_ma_sum,
  type = "Unstandardized", 
  x_var = "Intrinsic",
  parameters = c("wy2 ~ wx1", "wx2 ~ wy1"),
  lavaan = FALSE
) + 
  theme(axis.title.x = element_blank()) -
  forest_plot(
    object = fit_ma_sum,
    type = "Unstandardized", 
    x_var = "Extrinsic",
    parameters = c("wy2 ~ wx1", "wx2 ~ wy1"),
    lavaan = FALSE
  ) +
  plot_layout(nrow = 2)
ggsave(
  here("Output/Figures/Figure-MA-WB-Motivations.png"), 
  width = 8, 
  height = 8
)
```

## Other models

A pretty basic multilevel model.

```{r}
# Within and between components of each variable
# Done by game
d_model <- d %>%
  select(
    Game, pid, wid, Wave, Hours, SPANE, CSAS, 
    Intrinsic = Enjoyment, Extrinsic
  ) %>%
  arrange(Game, pid, Wave) %>% 
  group_by(Game, pid) %>% 
  mutate(
    across(
      c(Hours, Intrinsic, Extrinsic), 
      .fns = list(lag = ~lag(.)))
  ) %>% 
  ungroup() %>% 
  pivot_longer(
    c(SPANE, CSAS), 
    names_to = "Outcome", values_to = "y"
  ) %>%
  pivot_longer(
    c(Hours, Intrinsic, Extrinsic, ends_with("_lag")), 
    names_to = "Predictor", values_to = "x"
  ) %>% 
  group_by(Game, Predictor) %>% 
  group_split() %>% 
  map(
    ~bmlm::isolate(
      ., 
      by = "pid", 
      value = "x", 
      which = "both"
    )
  ) %>% 
  bind_rows()
```

```{r}
tmp <- d_model %>%
  group_by(Game, Outcome, Predictor) %>%
  summarise(
    tidy(
      lmer(y ~ x_cb + x_cw + (1 | pid), data = cur_data()), 
      "fixed", 
      conf.int = TRUE
    )
  )
tmp %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(estimate, Game, col = term)) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  geom_pointrangeh(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge2v(.4)
  ) +
  facet_grid(Predictor~Outcome)

tmp2 <- d_model %>%
  group_by(Outcome, Predictor) %>%
  summarise(
    tidy(
      lmer(y ~ x_cb + x_cw + (1 | Game/pid), data = cur_data()), 
      "fixed", 
      conf.int = TRUE
    )
  )
tmp %>% 
  ungroup() %>% 
  bind_rows(
    tmp2 %>% 
      mutate(Game = ".Average")
  ) %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(estimate, Game, col = term, shape = abs(statistic)>2)) +
  geom_vline(xintercept = 0, lty = 2, size = .25) +
  geom_pointrangeh(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge2v(.4)
  ) +
  facet_grid(Predictor~Outcome)
```

